%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Javascript, NodeJS, MongoDB, ReactJS, D3.js, Google App Engine, CircleCI} % Job title
    {Sumus Properties Group Ltd. | Software Developer (Part-Time)} % Organization
    {Remote} % Location
    {Oct. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improving iteration and delivery cycle of upcoming product by building out development and deployment tooling}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Golang, Javascript, ReactJS, D3.js, Graph Databases, Elasticsearch, MongoDB, Jenkins} % Job title
    {Riot Games, Inc. | Software Engineer Intern} % Organization
    {Los Angeles, California} % Location
    {May 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote and published an RFC for defining alerts in our service specification by driving a cross-team design effort}
        \item{Laid the groundwork for improved cross-region service visibility and integration with new metrics vendors by \\implementing and deploying the new specification, which saw use by 20+ services within the first month}
        \item {Improved how operators do root cause diagnosis of alerts across microservices by building an alert visualization web app and data pipeline to link alerts based on similarities (such as network topography)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Golang, gRPC, Docker, PostgreSQL, Travis CI, Tesseract} % Job title
    {RTrade Technologies Ltd. | Software Engineer (Part-Time)} % Organization
    {Remote} % Location
    {Sep. 2018 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a new product by implementing a service to orchestrate nodes for isolated peer-to-peer distributed filesystems}
        \item {Improved results and performance for our search engine by revamping it, adding a gRPC API, and integrating OCR}
        %\item {Created a docker-compose framework and suite of scripts for deploying production-like environments anywhere for integration testing, increasing the number of codebases with integration coverage by 8x}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Javascript, NodeJS, PostgreSQL, ReactJS, Python, Elasticsearch} % Job title
    {Michael Smith Genome Sciences Centre | Bioinformatics Co-op} % Organization
    {Vancouver, British Columbia} % Location
    {Jan. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced average data load times by 80\%+ and enabled new data views and reports by building a new Node.js server that became the core of the team’s 4 DNA analysis workflows and 3 websites}
        \item {Enabled visibility into the performance our analysis pipelines by setting up an Elasticsearch and APM deployment}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
